Технология использования открытых данных Федеральной налоговой службы России для экономико-географического анализа

### 2025-02-06 legal-services-provision/conference-paper/Paper.Rmd
Rename folder, #2
Reorganise files and adjust code for paper about legal services provision, #6

---
title: "UDC 911.3"
subtitle: "Concentration of Legal Companies and Accessibility of Legal Services: Empirical Evidence from Russian Cities"
output:
  word_document:
    reference: reference.docx
bibliography: biblio.bib
csl: biblio-style.csl
---

@@

```{r imports, include=FALSE, cache = TRUE}
library(here)
source(here("common", "Script.R"))
```

>>>>

---
title: "UDC 911.3"
subtitle: "Concentration of Legal Companies and Accessibility of Legal Services: Empirical Evidence from Russian Cities"
output:
  word_document:
    reference: assets/reference.docx
bibliography: assets/biblio.bib
csl: assets/biblio-style.csl
---

@@

```{r imports, include=FALSE, cache = TRUE}
source("helpers/Script.R")
```

### 2025-02-06 legal-services-provision/journal-article/Paper.Rmd
Reorganise files and adjust code for paper about legal services provision, #6

---
output:
  word_document:
    reference: reference.docx
bibliography: refs.bib
csl: style.csl
---

@@

```{r imports, include=FALSE, cache = TRUE}
source(here("journal-article", "Script.R"))
```

>>>>

---
output:
  word_document:
    reference: assets/reference.docx
bibliography: assets/refs.bib
csl: assets/style.csl
---

@@

```{r imports, include=FALSE, cache = TRUE}
source("helpers/Script.R")
```
